True versus apparent shapes of astrophysical bow shocks

### 2017-04-17 papers/Paper1/quadrics-appendix.tex
Include the linear p-value graph too, and redo fig caption

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/p-value-histogram}
  \caption{Histogram of \(p\)-values for all Anderson--Darling
    non-parametric 2-sample tests performed during the analysis of
    section~\ref{sec:comp-with-observ}.  The vertical dashed lines
    shows the traditional threshold values for significance:
    \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
    expected uniform distribution of \(p\)-values that would be
    expected if the null hypothesis were always true, that is, if no
    significant correlations existed.}
  \label{fig:histo-p-values}
\end{figure}

>>>>

\begin{figure}
  (a)\\
  \includegraphics[width=\linewidth]{figs/p-value-histogram-new-linear}\\
  (b)\\
  \includegraphics[width=\linewidth]{figs/p-value-histogram-new}
  \caption{Histogram of \(p\)-values for all non-parametric 2-sample
    tests performed during the analysis of
    section~\ref{sec:comp-with-observ}. (a)~Uniformly spaced linear
    bins and linear vertical axis. (b)~Uniformly spaced logarithmic
    bins and logarithmic vertical axis, with all values
    \(p \le 10^{-6}\) included in the leftmost bin.  The vertical dashed
    lines shows the traditional threshold values for significance:
    \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
    uniform distribution of \(p\)-values that would be expected if the
    null hypothesis were always true, that is, if no significant
    correlations existed.}
  \label{fig:histo-p-values}
\end{figure}
